Corrections

### 2020-10-22 reply.tex
getting closer

Both referees made great comments that I feel improve the manuscript
substantially, and I would like to thank them for that. I followed up
on every point made. The referees' comments and my replies are listed
below. Below, my replies are colored \ydnote{cyan}. In the revised
manuscript, replies to referee two are in \reftwo{green} and replies
to referee three are in \refthree{red}. Again, thank you for taking
the time and helping me improve this manuscript.

\section{Referee 1}
Preliminary Assessment, Editorial Board Membe.r The manuscript can be
sent to reviewers.

@@

\begin{enumerate}
\item It should be stated in the Abstract whether the work in this
  paper pertains to only linear inverse problems, or if it is
  applicable in general to non-linear inverse problems as well.
  \ydnote{\item Title and abstract now reflect the fact that the paper only
    pertains to linear inverse problems.}

\item It is unclear from the contribution section of the article what
exactly the primary contribution is. This should be stated very
explicitly and emphasized clearly as the contribution of the article.

\item In some equations (as seen below in the line comments) operators
are not clearly defined or described before they are given in a
proposition or theorem. Please clearly define all operators both with
mathematical definitions and descriptions (when applicable) before
using them.
\ydnote{\item Corrected, thanks!}

\item Overall, I find the article difficult to follow. I think this can
be improved by properly defining all operators and including section
overviews that give a description of the purpose of each section, and
a brief summary of how this is being accomplished.
\ydnote{\item Added section overviews and operator definitions.}

@@

The author should clearly state why one should consider
infinite-dimensional formulation of the observation operator? One
could just merge the observation operator into the forward simulation
operator, and follow standard formulations adopted by the works in the
references below. Moreover, when it comes to sensor placement,
observations are almost surely pointwise in space/time. In this case,
I don't see the benefit of consider infinite-dimensional formulation.

\ydnote{I was not able to arrive at the same results when the forward
  and observation operators were merged. A short remark on this was
  added. It is placed after equation (2.6) in the highlighted text
  (equation (2.5) in the new clean text. Specifically, we need it in
  equation (3.1).}

@@

\item The statement made on page 2, lines 40-41 (... apply equally to
  any of the scenarios...) is rather strong and unjustified.
\end{enumerate}

On page 8, Equation 4.2, which is crucial in this study, assumes that
the forward operator is invertible. This is clearly impossible in
practical Bayesian inverse problems, otherwise, it reduces to a
standard regression problem. This is understandable for clarification,
however, the following argument on Page 9 that extends this assumption
is not well-justified.
\ydnote{This is a great point! The flawed explanation was removed. I
  was able to remove that assumption.}

In Equation 4.3, not sure what $\fwd^{-*}$ stands for. Moreover, an
inverse of the forward operator is not well-defined even if
$\mathcal{F}\Gamma_{prior}\mathcal{F}^*$ is invertible! This is very
limiting, and can't be used in practical inverse problems. This should
be clearly discussed for the reader to appreciate the valuable effort
made.
\ydnote{Again, great point. $\fwd^{-*} = (\fwd^*)^{-1}$ but now I do
  not assume $\fwd$ is invertible so this is removed}

A numerical example with the setup studied in the paper, should help
clarify several confusions that a reader can fall for easily.

@@

In the abstract (line 20, page 1), and on page 5, lines 30-40, the
author mentions that the effect of observation-correlations on sensor
clusterization will be considered later, but I failed to find any
relevant discussion to that issue which I find interesting. Even if
the model error covariance $\Gamma_{model}$ is known, this doesn't
amount for observation correlations, .e.g,
single-instrument-observations, because the observation operator
$\mathcal{O}$ is non invertible. This issue should addressed and
clarified clearly.

I found it difficult to trace the referenced Lemmas, Corollaries,
etc., mainly because bad referencing in the appendix, and the links do
not works properly.  For example Corollary 2 should be Corollary B.x,
etc.
\ydnote{All such bad references were fixed.}

@@

Sensor clusterization in OED is central to this study. Figure 2 is
used to illustrate the phenomena, however, it is underrepresented, and
is hard to decipher. Specifically, Section 4.2 (Page 10, lines 36-39),
and caption of Figure 2 should be rewritten with clear explanation of
the axes, and the plot-generation process.

One page 10, lines 30-35, the argument doesn't seem to be quite
accurate. It's not always true that one associates a higher
weight/value to ``better'' observation. If one defines ``better'' as
lower uncertainty, then, variable observation variances must be
considered. On the other hand, if being ``better'' corresponds to a
more accurate realization of the observation (true snapshot of
reality), then the whole statement would be wrong, because optimal
design relies only on the uncertainty levels in linear Bayesian
settings, as manifested by the posterior covariance matrix.

The last statement of the proof of Lemma A.1 (see page 12, line 24),
stating that ``there is nothing special about $t=0$, and the relation
holds for all t''. This is rather odd. In fact, It is assumed that
$X(t=0)$ explicitly (see line 32 on page 11). A clarification is
required here.

@@

Page 1, line 22; ... ``calculating derivative of log det of
oeprators''. Please clarify for the reader, which operators you're
referring to.

Page 2, line 11; wrong reference to Figure 1.3?

Page 6; in equation 2.7, don't you need an expectation over all priors
to achieve this result? Please clarify.

Page 6, line 13; the optimization problem is solved for $\mathcal{O}$,
not $\Psi$ ?

Page 6, lines 19; the statement made about relaxing the constraints on
the observation operator is unclear.

Page 6, line 24, I believe the reference to (3.2) should be replaced
with (3.1).

Page 6, line 26, proof is provided in which Appendix? Please state
clearly.

page 6, In the proof of Lemma 3.1, the author utilized the operator
$T$, which is only introduced in the appendix (Proof of Lemma
A.1). Maybe state that clearly here. Also, in the proof, from step 4
to 5, the first and third terms vanished; why?

Page 7; Proposition 1 should be replaced with something like
Proposition 3.2 or something similar to match previous referencing
(e.g., Lemma 3.1).

Page 7, line 27 (and also line 31); the reference to Proposition 2
seems to be incorrect. Also, state clearly which appendix the proof is
delegated to.

Page 10, Corollary 1 should be renamed (see the comment on Proposition
1 above). Same applies to Corollary 3 in the appendix. Better also to
clarify which appendix. Finally, the author utilizes
$\widehat{\Gamma_{post}}$ int the corollary, which is defined only in
the appendix, under the proof.

Page 11, in the proof of Lemma A.1 (lines 39-43), the partial
derivative vanished from step 2 to step 3; please explain!

>>>>

Both referees made great comments that I feel improve the manuscript
substantially, and I would like to thank them for that. I followed up
on every point made. The referees' comments and my replies are listed
below. My replies are colored \textcolor{cyan}{cyan}. Again, thank you
for taking the time and helping me improve this manuscript.

\section{Referee 1}
Preliminary Assessment, Editorial Board Member The manuscript can be
sent to reviewers.

@@

\begin{enumerate}
\item It should be stated in the abstract whether the work in this
  paper pertains to only linear inverse problems, or if it is
  applicable in general to non-linear inverse problems as well.
  \ydnote{Title and abstract now reflect the fact that the paper only
    pertains to linear inverse problems.}

\item It is unclear from the contribution section of the article what
exactly the primary contribution is. This should be stated very
explicitly and emphasized clearly as the contribution of the article.
\ydnote{The contribution section was extended.}

\item In some equations (as seen below in the line comments) operators
are not clearly defined or described before they are given in a
proposition or theorem. Please clearly define all operators both with
mathematical definitions and descriptions (when applicable) before
using them.
\ydnote{Corrected, thanks!}

\item Overall, I find the article difficult to follow. I think this can
be improved by properly defining all operators and including section
overviews that give a description of the purpose of each section, and
a brief summary of how this is being accomplished.
\ydnote{Added section overviews and operator definitions.}

@@

The author should clearly state why one should consider
infinite-dimensional formulation of the observation operator? One
could just merge the observation operator into the forward simulation
operator, and follow standard formulations adopted by the works in the
references below. Moreover, when it comes to sensor placement,
observations are almost surely pointwise in space/time. In this case,
I don't see the benefit of consider infinite-dimensional formulation.
\ydnote{I was not able to arrive at the same results when the forward
  and observation operators were merged. A short remark on this was
  added. It is placed after equation (2.6) in the highlighted text
  (equation (2.5) in the new clean text. Specifically, we need it in
  equation (3.1).}

@@

\item The statement made on page 2, lines 40-41 (... apply equally to
  any of the scenarios...) is rather strong and unjustified.
  \ydnote{Said statement was removed.}
\end{enumerate}

On page 8, Equation 4.2, which is crucial in this study, assumes that
the forward operator is invertible. This is clearly impossible in
practical Bayesian inverse problems, otherwise, it reduces to a
standard regression problem. This is understandable for clarification,
however, the following argument on Page 9 that extends this assumption
is not well-justified.  \ydnote{This is a great point! The flawed
  explanation was removed. I was able to remove that assumption. But
  it required further changes to the manuscript.}

In Equation 4.3, not sure what $\fwd^{-*}$ stands for. Moreover, an
inverse of the forward operator is not well-defined even if
$\mathcal{F}\Gamma_{prior}\mathcal{F}^*$ is invertible! This is very
limiting, and can't be used in practical inverse problems. This should
be clearly discussed for the reader to appreciate the valuable effort
made. \ydnote{Again, great point. $\fwd^{-*} = (\fwd^*)^{-1}$ but now
  I do not assume $\fwd$ is invertible so this was removed.}

A numerical example with the setup studied in the paper, should help
clarify several confusions that a reader can fall for easily.
\ydnote{I added several plots that I believe make the arguments and
  conclusions clearer. I also added an illustration story with
  graduated lab cylinders.}

@@

In the abstract (line 20, page 1), and on page 5, lines 30-40, the
author mentions that the effect of observation-correlations on sensor
clusterization will be considered later, but I failed to find any
relevant discussion to that issue which I find interesting.
\ydnote{The discussion on observation correlation
  and how it mitigates clusterization can be found in the last
  section.}

Even if the model error covariance $\Gamma_{model}$ is known, this
doesn't amount for observation correlations, .e.g,
single-instrument-observations, because the observation operator
$\mathcal{O}$ is non invertible. This issue should addressed and
clarified clearly.  \ydnote{I am not sure I understand this
  point. $\modcov$ can model anything you want, including correlated
  observation instruments. It is true that $\obs$ is not invertible
  but I fail to understand why this is problematic.}

I found it difficult to trace the referenced Lemmas, Corollaries,
etc., mainly because bad referencing in the appendix, and the links do
not works properly.  For example Corollary 2 should be Corollary B.x,
etc.  \ydnote{All such bad references and links were fixed.}

@@

Sensor clusterization in OED is central to this study. Figure 2 is
used to illustrate the phenomena, however, it is underrepresented, and
is hard to decipher. Specifically, Section 4.2 (Page 10, lines 36-39),
and caption of Figure 2 should be rewritten with clear explanation of
the axes, and the plot-generation process.  \ydnote{I extended the
  discussion relating to clusterization, added another plot and
  explained how they arise.}

On page 10, lines 30-35, the argument doesn't seem to be quite
accurate. It's not always true that one associates a higher
weight/value to ``better'' observation. If one defines ``better'' as
lower uncertainty, then, variable observation variances must be
considered. \ydnote{Unfortunately, I am again not sure I understand
  fully. Variable observation variances are fixed to $\sigma^2$
  througout this section.}

On the other hand, if being ``better'' corresponds to a more accurate
realization of the observation (true snapshot of reality), then the
whole statement would be wrong, because optimal design relies only on
the uncertainty levels in linear Bayesian settings, as manifested by
the posterior covariance matrix.  \ydnote{I think the referee implies
  that the D-optimal design is only as good as the assumptions it
  relies on. I could not agree more. However, as long as we do believe
  the assumptions made --- a D-optimal design is indeed optimal (in a
  precise and quantifiable way). I think the source of
  misunderstanding is that I used the term ``measurement'' where I
  should have used ``eigenvector''. I changed the paragraph
  accordingly. The transition from thinking of ``measurements'' to
  thinking of ``eigenvectors'' is confusing and I believe it is better
  explained in the updated version of the manusctipt.}

The last statement of the proof of Lemma A.1 (see page 12, line 24),
stating that ``there is nothing special about $t=0$, and the relation
holds for all t''. This is rather odd. In fact, It is assumed that
$X(t=0)$ explicitly (see line 32 on page 11). A clarification is
required here.  \ydnote{Clarification was added at the end of the
  proof. ``There is nothing special about $t=0$'' means we could have
  chosen any other value $t_0$ instead.}

@@

Page 1, line 22; ... ``calculating derivative of log det of
oeprators''. Please clarify for the reader, which operators you're
referring to.
\ydnote{Made explicit.}

Page 2, line 11; wrong reference to Figure 1.3?  \ydnote{Reference now
  fixed.}

Page 6; in equation 2.7, don't you need an expectation over all priors
to achieve this result? Please clarify.
\ydnote{The expectation / integration over the prior space happens
  inside the KL divergence:
  $$
  \mathbb{E}_{\data}[KL(\post^\data||\pr)] = \int KL(\post^\data||\pr) \der \mu(\data) = \int \int \log \frac{\der \post^\data}{\der \pr}(x) \der \post(x) \der \mu(\data)
  $$ where $\mu(\data)$ is the distribution of data (usually called
  evidence). I improved the notation to reflect the dependence of the
  posterior on the data $\data$. I added above definition of KL
  divergence to the manuscript.}

Page 6, line 13; the optimization problem is solved for $\mathcal{O}$,
not $\Psi$ ?  \ydnote{This line was unclear. I extended the
  explanation. The mauscript now reflects the claim that the optimal
  $\obs^{\star}$ is the maximizer of $\tar(\obs)$.}

Page 6, lines 19; the statement made about relaxing the constraints on
the observation operator is unclear.  \ydnote{This sentence was poorly
  written. It is now rephrased.}

Page 6, line 24, I believe the reference to (3.2) should be replaced
with (3.1). \ydnote{This was actually OK. The gradient was recorded in
  (3.2).}

Page 6, line 26, proof is provided in which Appendix? Please state
clearly.
\ydnote{Fixed.}

page 6, In the proof of Lemma 3.1, the author utilized the operator
$T$, which is only introduced in the appendix (Proof of Lemma
A.1). Maybe state that clearly here. Also, in the proof, from step 4
to 5, the first and third terms vanished; why?  \ydnote{This point is
  spot on. I added the definition of $T$ before the derivation. This
  is not the proof of Lemma 3.1 --- it is the first variation of the
  objective. I reworded a few sentences to make this clearer.}

Page 7; Proposition 1 should be replaced with something like
Proposition 3.2 or something similar to match previous referencing
(e.g., Lemma 3.1). \ydnote{Fixed.}

Page 7, line 27 (and also line 31); the reference to Proposition 2
seems to be incorrect. Also, state clearly which appendix the proof is
delegated to.  \ydnote{Fixed.}

Page 10, Corollary 1 should be renamed (see the comment on Proposition
1 above). Same applies to Corollary 3 in the appendix. Better also to
clarify which appendix. Finally, the author utilizes
$\widehat{\Gamma_{post}}$ int the corollary, which is defined only in
the appendix, under the proof. \ydnote{All comments on numbering and
  references are great and correct. All were fixed. I added an
  explanation of what $\widehat{\Gamma_{post}}$ means where it
  appears.}

Page 11, in the proof of Lemma A.1 (lines 39-43), the partial
derivative vanished from step 2 to step 3; please explain!
\ydnote{I added an extra equality line for explanation.}
